---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pdfsplit

<!-- badges: start -->
[![R-CMD-check](https://github.com/Mubarak-M/pdfsplit/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Mubarak-M/pdfsplit/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The `pdfsplit` package provides functions for extracting pages from PDF
 files based on keyword(s). Using the [pdftools](https://github.com/ropensci/pdftools)  package developed by [rOpenSci](https://ropensci.org/), pdf pages can be extracted from in R 
 environment without the need for additional setup. 

## Installation

You can install the development version of pdfsplit from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Mubarak-M/pdfsplit")
```
## Usage
This package currently offers two functions that are beneficial to users. The first, `keyword_split`, is designed to extract page(s) based on keywords from a single PDF file. The second function, `directory_split`, performs a similar task but operates on an entire directory of PDF files.

### Example with `keyword_split`
The package includes two PDF files sourced from [arXiv](https://arxiv.org/) for use as test cases. Here is an example demonstrating the use of the `keyword_split` function.


#### Extract pages based on a single keyword
```{r, eval=FALSE}
file <- system.file("extdata", "1406.4806.pdf", package = "pdfsplit")
pdf_file <- file.path(getwd(), "output.pdf")
keyword_split(file,keyword = "test", file_output = pdf_file)
```

#### Extract pages based on a single keyword
```{r, eval=FALSE}
file <- system.file("extdata", "1406.4806.pdf", package = "pdfsplit")
pdf_file <- file.path(getwd(), "output.pdf")
keyword_split(file,keyword = c("test","performance"), file_output = pdf_file)
```

### Example with `directory_split`
The `directory_split` function enables users to extract pages using specified keywords across multiple PDF files in a single function call. It offers the same functionality found in the `pdf_split` function. Below is an example demonstrating the extraction within a single directory.

```{r, eval=FALSE}
directory <- system.file("extdata", package = "pdfsplit")
dir_outs <- file.path(getwd(),"output")
directory_split(directory,keyword = "test", dir_output = dir_outs)
```

## Limitations

The package currently does not support scanned PDF files that require OCR (Optical Character Recognition) for text recognition.
